%{\Large Acknowledgements} \\
{\large\chapter*{Acknowledgements}\label{sec:Acknowledgements}}\addcontentsline{toc}{chapter}{Acknowledgements}
\hrule

The success and undertaking of this project would not be possible without an instrumental role and support by many people. 

I would like to sincerely thank Dr M.Y. Abdul Gaffar for the countless hours of supervision, encouragement and being a source of knowledge and ideas that played such a significant role in the process of conducting this project. Without your guidance, the project would not have been a success.

To my co-supervisor, Mr J. Son, thank you for taking in an additional student and for aiding the project by offering advice while being a soundboard for ideas.

Thank you to Mr J. Pead for the guidance on electronics selection and practical questions that I had. You provided me with the necessary tools to succeed. Thank you to Chiao-Shing 'Charlie' Lin for your quick email responses and ideas that helped shape the project into what it is today. Also thank you to Denielle Rawthee and Riselle Rawthee for doing work over your holiday period to aid my decision making during project.

Without the support and help of my colleagues, the project would have gone a different direction. I would like to thank each friend that offered a listening ear when something inevitably went wrong.

To my family and friends, thank you for the confidence that you displayed in my abilities. My parents for making this all possible, Matthew who helped and supported me whenever I needed help and ideas. Thank you to Mia who stood by and supported me throughout the project, my studies and life. 



%Many people were instrumental in the success of this project and being helpful in the undertaking of this project.

%, thank you for your support, guidance, encouragement and supervision.

%My family, your confidence in me and my abilities greatly helped keep my ambitions high and stress at a manageable level.

%		funders → supervisors → other academics → colleagues → family and friends

\newpage