{\smallest\chapter*{Terms of Reference}\label{chap:Terms of Reference}}\addcontentsline{toc}{chapter}{Terms of Reference}\\
\hrule
\subsubsection*{Title}
Development of a small-scale, educational, low-cost embedded audio radar system for demonstration purposes.
\subsubsection*{Description}
Radar systems are generally a concept that is not accessible to the masses without prior knowledge about the workings of radar. The high frequencies that radar usually work at are not audible and therefore, not tangible for the layperson. In an attempt to bridge the gap between the inexperienced and the university student with basic knowledge of how radar operates, the low-cost audio radar system would be developed. The radar system operated in the audible range to produce a tangible result.
\subsubsection{Deliverables}
The items that are expected upon the completion of the project include:
\begin{enumerate}
\item 	a working audio radar system to be used at university open-days.
\item 	a manual on how to build and program the radar to be easily reproducible by university students.
\item 	a manual on how to operate the completed radar system.
\item 	a full report that outlines the design and development of the system as a whole and all subsystems.
\end{enumerate}
\subsubsection*{Requirements and Skills}
Interfacing between software and hardware (electronics), Programming, Radar Theory.
\subsubsection*{Area}
Education, Radar Systems, Embedded Systems and Technology
\fancyfoot[C]{\thepage}
\pagestyle{plain}
\newpage